Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-04-27 writeup/gz_hubble_data.tex
Finishing Cassata/Tasca

Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}.

>>>>

Using a 0.5\arcsec{} positional match, we find 76,241 galaxies with morphologies in both GZH and \citet{cas07}. At the lowest values of \pbest, $\sim10\%$ of the \citet{cas07} galaxies are classified as irregular, only $\sim30\%$ as early-type, and $60\%$ as spiral. The early-type fraction drops with increasing \pbest, with an increasing proportion of irregulars. The \podd{} vote fraction distinguishes sharply between spirals and irregulars at \podd$>0.2$.

Despite using a similar classification method to \citet{cas07}, the \citet{tas11} classifications show significantly different trends as a function of GZH classifications. Spiral galaxies consistently make up $\sim60\%$ of the sample at \emph{all} \pbest, with a mild increase at \pbest$\simeq1.0$. Early-type and irregular galaxies make up the remainder, smoothly varying between irregulars at low \pbest{} and early-types and high \pbest.
